Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-02-26 code/paper.Rmd
maps

# all WH sites with WP pages (n = 584)
page_data_for_all_pages <- readRDS("data/page_data_for_all_pages.rds")

# all WH sites, with and without WP pages (n = 846)
wh_wiki_table <- read_csv('data/wh_wiki_table.csv')

@@

```{r}
library("rnaturalearth")
library("rnaturalearthdata")
world <- ne_countries(scale = "medium", returnclass = "sf")

  # get country of site from location text
  # Laos, Czech Republic, Micronesia, Zimbabwe, South Sudan, Chad, 
  # Central African Republic, Congo, Gabon, Cameroon, Nigeria, Bosnia and Herzegovina
  #  Cote d'Ivoire, Sierra Leone, Guyana, Belize, 
  country_names <-  paste(c(world$name, 
                            "United States",
                            "Czech Republic",
                             "Antigua & Barbuda",
                            "Saint Kitts and Nevis"
                            ),
                          collapse="|")

@@

```{r}
sf_map_data <- 
world %>% 
  filter(name != "Antartica") %>% 
  left_join(wh_wk_country_counts,
            by = c( 'name' = 'country')) %>% 
  select(name, n, geometry)

wh_wk_country_count_map <- 
ggplot(data = sf_map_data) +
    geom_sf(aes(fill = n)) +
    scale_fill_viridis_c(na.value="grey90") +
  coord_sf() +
  theme_minimal()
```

Combine map and histogram

```{r}
wh_wk_country_count_map +
  annotation_custom(ggplotGrob(wh_wk_country_counts_hist), 
                    xmin = -190, 
                    xmax = -90, 
                    ymin= 10, 
                    ymax=-70) 
```

@@

wh_wk_country_prop_scatter <- 
ggplot(wh_wk_country_all_counts,
       aes(prop_sites_with_pages, n)) +
  geom_point() +
  coord_fixed(0.02) +
  theme_nogrid(6)

@@

sf_map_data_prop <- 
world %>% 
  filter(name != "Antartica") %>% 
  left_join(wh_wiki_table_location_prop,
            by = c( 'name' = 'country')) %>% 
  select(name, prop_sites_with_pages, geometry)

wh_wk_country_prop_map <- 
ggplot(data = sf_map_data_prop) +
    geom_sf(aes(fill = prop_sites_with_pages)) +
    scale_fill_viridis_c(na.value="grey90") +
  coord_sf() +
  theme_minimal()

@@

>>>>

# all WH sites with WP pages (n = 584)
page_data_for_all_pages <- 
  readRDS(here::here("data", 
                     "page_data_for_all_pages.rds"))

# all WH sites, with and without WP pages (n = 846)
wh_wiki_table <- 
  read_csv(here::here("data", 
                      "wh_wiki_table.csv"))

# all WH sites according to UNESCO
# from https://whc.unesco.org/en/syndication
wh_unesco <- readxl::read_excel(here::here("data",
                                           "whc-sites-2018.xls")) %>% 
  filter(category %in% c("Cultural", "Mixed"))

library("rnaturalearth")
library("rnaturalearthdata")
world <- ne_countries(scale = "medium", returnclass = "sf")

# functions used more than once:

theme_nogrid <- function (base_size = 12, base_family = "") {
  theme_bw(base_size = base_size, 
           base_family = base_family) %+replace% 
    theme(panel.grid = element_blank() )   
}
```

## Representation by country

Where are the WH sites, before looking into WP

wh_unesco_countries <- 
wh_unesco %>% 
  separate_rows(states_name_en, convert = TRUE, sep = ",") %>% 
  mutate(country = case_when(
    states_name_en == "Bolivia (Plurinational State of)"  ~ "Bolivia",
    states_name_en == "Cabo Verde"  ~ "Republic of Cabo Verde",
    states_name_en == "Czechia"  ~ "Czech Republic",
    states_name_en == "Democratic People's Republic of Korea"  ~ "Republic of Korea",
    states_name_en == "Gambia (the)"  ~ "The Gambia",
    states_name_en == "Holy See"  ~ "Vatican",
    states_name_en == "Iran (Islamic Republic of)"  ~ "Iran",
    states_name_en == "Lao People's Democratic Republic"  ~ "Lao PDR",
    states_name_en == "Micronesia (Federated States of)"  ~ "Federated States of Micronesia",
    states_name_en == "Syrian Arab Republic"  ~ "Syria",
    states_name_en == "the former Yugoslav Republic of Macedonia"  ~ "Macedonia",
    states_name_en == "United Kingdom of Great Britain and Northern Ireland"  ~ "United Kingdom",
    states_name_en == "United Republic of Tanzania"  ~ "Tanzania",
    states_name_en == "United States of America"  ~ "United States",
    states_name_en == "Venezuela (Bolivarian Republic of)"  ~ "Venezuela",
    states_name_en == "United States of America"  ~ "United States",
    states_name_en == "Viet Nam"  ~ "Vietnam",
    states_name_en == "Republic of Moldova"  ~ "Moldova",
    TRUE ~ as.character(states_name_en)
  ))

wh_unesco_countries_count <-  
  wh_unesco_countries %>% 
  count(country)

median_number_unesco_sites_per_country <- 
  median(wh_unesco_countries_count$n)

mode_number_unesco_sites_per_country <- 
  round(estimate_mode(wh_unesco_countries_count$n), 1)

wh_unesco_country_counts_hist <- 
ggplot(wh_unesco_countries_count,
       aes(n)) +
  geom_histogram() +
  annotate("text", x = 30, y = 30, 
           label = str_glue('Median = {median_number_unesco_sites_per_country} WH sites/country\nMode = {mode_number_unesco_sites_per_country} WH sites/country'),
           size = 3) +
  theme_nogrid(12)

sf_map_data_unesco <- 
world %>% 
  left_join(wh_unesco_countries_count,
            by = c( 'name_long' = 'country')) %>% 
  select(name, n, geometry) %>% 
  mutate(n = ifelse(is.na(n), 0, n)) %>% 
  filter(name != "Antartica")

wh_country_unesco_count_map <- 
ggplot(data = sf_map_data_unesco) +
    geom_sf(aes(fill = n), lwd = 0) +
    scale_fill_viridis_c(na.value="grey90") +
  coord_sf() +
  coord_sf(ylim = c(-50, 90), datum = NA) +
  theme_minimal()

wh_country_unesco_count_map +
  annotation_custom(ggplotGrob(wh_unesco_country_counts_hist), 
                    xmin = -190, 
                    xmax = -90, 
                    ymin= 10, 
                    ymax=-70)

@@

```{r}
  # get country of site from location text
  # Laos, Czech Republic, Micronesia, Zimbabwe, South Sudan, Chad, 
  # Central African Republic, Congo, Gabon, Cameroon, Nigeria, Bosnia and Herzegovina
  #  Cote d'Ivoire, Sierra Leone, Guyana, Belize, 
  country_names <-  paste(c(world$name, 
                            "United States",
                            "Czech Republic",
                             "Antigua & Barbuda",
                            "Saint Kitts and Nevis"
                            ),
                          collapse="|")

@@

```{r}
sf_map_data <- 
world %>% 
  left_join(wh_wk_country_counts,
            by = c( 'name' = 'country')) %>% 
  select(name, n, geometry) %>% 
  mutate(n = ifelse(is.na(n), 0, n)) %>% 
  filter(name != "Antartica")

wh_wk_country_count_map <- 
ggplot(data = sf_map_data) +
    geom_sf(aes(fill = n), lwd = 0) +
    scale_fill_viridis_c(na.value="grey90") +
  coord_sf() +
  coord_sf(ylim = c(-50, 90), datum = NA) +
  theme_minimal()

wh_wk_country_count_map +
  annotation_custom(ggplotGrob(wh_wk_country_counts_hist), 
                    xmin = -190, 
                    xmax = -90, 
                    ymin= 10, 
                    ymax=-70) 
```

@@

wh_wk_country_prop_scatter <- 
ggplot(wh_wk_country_all_counts,
       aes(prop_sites_with_pages, n)) +
  geom_point(alpha = 0.5) +
  coord_fixed(0.02) +
  theme_nogrid(6)

@@

sf_map_data_prop <- 
world %>% 
  filter(name != "Antartica") %>% 
  left_join(wh_wiki_table_location_prop,
            by = c( 'name' = 'country')) %>% 
  select(name, 
         prop_sites_with_pages, 
         geometry)  %>% 
  mutate(prop_sites_with_pages = ifelse(is.na(prop_sites_with_pages), 0, prop_sites_with_pages))

wh_wk_country_prop_map <- 
ggplot(data = sf_map_data_prop) +
    geom_sf(aes(fill = prop_sites_with_pages), lwd = 0) +
    scale_fill_viridis_c(na.value="grey90") +
  coord_sf() +
  coord_sf(ylim = c(-50, 90), datum = NA) +
  theme_minimal()

@@

## Basic qualities of the WP articles about WH sites

Length: correlate with ??
number of links out/word
number of references/word: scholarly or not

## Basic qualitites of attention paid to articles

number of links in
page_views_last_n_days_total

## Basic qualities of the editing process

number of edits, total, prop/words
size of edits
divesity of editors

## Locality

IP addresses

## Networks

editors

## Controversies

time between edits
edit reverts
talk page: length and sentiment

## Technicity

bots
